Columnar VCF for Biobank scale datasets using Zarr

### 2024-04-10 paper.tex
Update subset-matrix compute figures

\begin{figure}
\includegraphics{figures/whole-matrix-compute}
\caption{Whole-matrix compute performance with increasing sample size.
Total CPU time required to run \texttt{bcftools +af-dist}
and equivalent operations in a single thread for various tools.
Elapsed time is also reported (dotted line). Run-time for genozip
at $10^6$ samples was extrapolated by fitting an exponential.
\label{fig-whole-matrix-compute}}
\end{figure}

@@

\begin{figure}
\includegraphics[width=6cm]{figures/subset-matrix-compute}
\caption{Compute performance on subsets of the matrix.
(A) Total CPU time required to run the afdist calculation for
a subset of 10 samples and 10000 variants from the middle of the matrix.
(B) Same for n/2 samples. Genozip did not run in this case for
$n > 10^4$ samples because it does not support a file to specify
sample IDs, and the command line was therefore too long for the shell
to execute. [TODO Note that in this case the bcftools pipeline requires
an additional step to compute AF etc.]
\label{fig-subset-matrix-compute}}
\end{figure}

@@

% \clearpage
% \renewcommand\thefigure{S\arabic{figure}}
% \setcounter{figure}{0}
% \renewcommand\thetable{S\arabic{table}}
% \setcounter{table}{0}

% \section*{Supplementary Material}

>>>>

\begin{figure}
\includegraphics{figures/whole-matrix-compute}
\caption{Whole-matrix compute performance with increasing sample size.
Total CPU time required to run \texttt{bcftools +af-dist}
and equivalent operations in a single thread for various tools.
Elapsed time is also reported (dotted line). Run-time for genozip
at $10^6$ samples was extrapolated by fitting an exponential.
See Methods for full details.
\label{fig-whole-matrix-compute}}
\end{figure}

@@

\begin{figure}
\includegraphics{figures/subset-matrix-compute}
\caption{Compute performance on subsets of the matrix.
Total CPU time required to run the af-dist calculation for
a subset of 10 samples and 10000 variants from the middle of the matrix
for the data in Figure~\ref{fig-data-storage}.
[TODO Note that in this case the bcftools pipeline requires
an additional step to compute AF etc.]
\label{fig-subset-matrix-compute}}
\end{figure}

@@

\clearpage
\renewcommand\thefigure{S\arabic{figure}}
\setcounter{figure}{0}
\renewcommand\thetable{S\arabic{table}}
\setcounter{table}{0}

\section*{Supplementary Material}

\begin{figure}
\includegraphics{figures/subset-matrix-compute-supplemental}
\caption{Compute performance on a large subset of the genotype matrix.
Total CPU time required to run the af-dist calculation for
a subset of half of the samples and 10000 variants from the middle of the matrix
for the data in Figure~\ref{fig-data-storage}.
Genozip did not run for
$n > 10^4$ samples because it does not support a file to specify
sample IDs, and the command line was therefore too long for the shell
to execute. 
\label{fig-subset-matrix-compute-supplemental}}
\end{figure}
